### 2020-01-31 README.Rmd
patch way duckdb calls disk storage location
duckdb was attempting in-memory location, since
`duckdb::duckdb()` does not seem to follow the `dbname` convention of MonetDBLite, RSQLite and others in passing the path for persistent storage.  cc @noamross

```{r}
most_synonyms <- taxa_tbl("col") %>% 
  group_by(acceptedNameUsageID) %>% 
  count(sort=TRUE)
most_synonyms
```
However, unlike the `filter_*` functions which return convenient in-memory tables, this is still a remote connection.  This means that direct access using the `taxa_tbl()` function (or directly accessing the database connection using `td_connect()`) is more low-level and requires greater care.  For instance, we cannot just add a `%>% mutate(acceptedNameUsage = get_names(acceptedNameUsageID))` to the above, because `get_names` does not work on a remote collection.  Instead, we would first need to use a `collect()` to pull the summary table into memory.  Users familiar with remote databases in `dplyr` will find using `taxa_tbl()` directly to be convenient and fast, while other users may find the `filter_*` approach to be more intuitive.

@@

```{r}
most_synonyms %>% 
  head(1) %>% 
  pull(acceptedNameUsageID) %>% 
  filter_id("col") %>%
  select(scientificName)
```

>>>>

```{r}
most_synonyms <- 
  taxa_tbl("col") %>% 
  count(acceptedNameUsageID, sort=TRUE)
most_synonyms
```
However, unlike the `filter_*` functions which return convenient in-memory tables, this is still a remote connection.  This means that direct access using the `taxa_tbl()` function (or directly accessing the database connection using `td_connect()`) is more low-level and requires greater care.  For instance, we cannot just add a `%>% mutate(acceptedNameUsage = get_names(acceptedNameUsageID))` to the above, because `get_names` does not work on a remote collection.  Instead, we would first need to use a `collect()` to pull the summary table into memory.  Users familiar with remote databases in `dplyr` will find using `taxa_tbl()` directly to be convenient and fast, while other users may find the `filter_*` approach to be more intuitive.

@@

```{r}
#most_synonyms %>% 
#  head(1) %>% 
#  pull(acceptedNameUsageID) %>% 
#  filter_id("col") %>%
#  select(scientificName)

filter_id("COL:43082445", "col")
```
